One more attempt on ArXe

### 2015-11-09 exp_results.tex

\begin{table}
\caption{Properties of the outer valence spectra of mixed ArXe clusters. Spectra of pure Ar and Xe clusters are included for reference. All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). Binding energies $E_b$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. The experimental Xe content of the clusters always is higher than in the original gas mixture (see Tab.\ \protect\ref{tab:cluster}). It was determined from the areas of the respective photolines, corrected by the respective atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}. Uncertainties are estimated as 3\,\% for the Xe content and 0.05~eV for the binding energies. Labels given in the first column refer to the expansion parameters in Tab.\ \protect\ref{tab:cluster}. $E_b$ and $w$ are in eV, $A$ is in \%. The binding energies can be compared to atomic values of 15.82~eV, 13.43~eV and 12.13~eV for Ar 3p and Xe 5p.
\label{tab:valence} }
\begin{tabular}{ l c c c c c c}
%
\toprule
  label & $E_b$(Ar 3p) & $w$(Ar 3p) & $E_b$(Xe 5p$_{1/2}$) &  $E_b$(Xe 5p$_{3/2}$) & $w$(Xe 5p$_{3/2}$)  &  $A$(Xe) \\
%
\midrule
% Ar, from Marko
 Ar (1) &  15.3  &  1.1 & & & &  \\
% Ar, from Marko 
 Ar (2) &  15.1  &  1.3 & & & &  \\
%
%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
% 1103 676, 679
 (a) & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
% 1103 670
 (b) & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
% 1103 671
 (c) & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
% 1103 663
 (d) & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
% 1103 640
 (e) & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
% 0506 
Xe (1) & & & 12.76 & 11.19 & 1.18 & 100\\
%
\midrule
%
%  1004  886  (UHe, c.g. + roi values)
 886 & 15.15 & 1.3 & 12.59 & 11.01 & 1.24 & 19\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{Properties of the outer valence spectra of mixed ArXe clusters. Spectra of pure Ar and Xe clusters are included for reference. All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). Binding energies $\EB$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. The experimental Xe content of the clusters (Xe$_{\rm cl}$) always is higher than in the original gas mixture (Xe$_{\rm in}$). Xe$_{\rm cl}$ was determined from the areas of the respective photolines, corrected by the respective atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}. Uncertainties are estimated as 3\,\% for the Xe content and 0.05~eV for the binding energies. $\EB$ and $w$ are in eV. The theoretical Ar 3p binding energy, averaged over fine structure, amounts to 15.27 eV.
\label{tab:valence} }
\begin{tabular}{ l c c c c c c c c}
%
\toprule
 \multicolumn{2}{r}{size} &  Xe$_{in}$& $\EB$ & $w$& \multicolumn{2}{c}{$\EB$}  & $w$ &  Xe$_{cl}$ \\
%
 \multicolumn{2}{r}{(label)}&  (\%) & (Ar 3p) & (Ar 3p) & (Xe 5p$_{1/2}$) &  (Xe 5p$_{3/2}$) & (Xe 5p$_{3/2}$)  &  (\%) \\
\midrule
% Ar, from Marko
 Ar & (1) &&  15.3  &  1.1 & & & &  \\
% Ar, from Marko 
 Ar & (2) &&  15.1  &  1.3 & & & &  \\
%
%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
% 1103 676, 679
 ArXe & S &1.2 & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
% 1103 670
 ArXe & M &1.2 & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
% 1103 671
 ArXe & L &1.2 & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
% 1103 663
 ArXe & S &3.0 & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
% 1103 640
 ArXe & M &5.0 & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
% 0506 
 Xe &  & & & & 12.76 & 11.19 & 1.18 & 100\\
%
\midrule
%
%  1004  886  (UHe, c.g. + roi values)
 ArXe & XL &2.5 & 15.15 & 1.3 & 12.59 & 11.01 & 1.24 & 19\\
%
\midrule
%
 Ar, Xe & th.\cite{Fasshauer13} && 14.76|15.53 && 12.53 & 10.83 &&\\
%
 \multicolumn{2}{r}{atomic\cite{velchev,sansonetti}} && 15.82 && 13.43 & 12.13 &&\\
%
\bottomrule
\end{tabular}
\end{table}
